Manuscript draft

### 2024-01-10 manuscript.qmd
switched to self-contained html for the manuscript

---
title: "Manuscript draft"
format: html
editor: visual
date: last-modified
author: Kaija Gahm, [others]
bibliography: references.bib
csl: the-american-naturalist.csl
---

>>>>

---
title: "Manuscript draft"
format:
  html:
    embed-resources: true
editor: visual
date: last-modified
author: Kaija Gahm, [others]
bibliography: references.bib
csl: the-american-naturalist.csl
---
